On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions

### 2013-10-11 paper2.tex
small changes

\begin{figure*} 
\centering
\includegraphics[width=0.85\textwidth]{figures/RLFs_1.4.eps}
\caption{RH luminosity function (RLF) at 1.4~GHz. The top left panel shows the
  RLF of our extended CR model (see main text for the details of the chosen
  parameters) for different fractions of radio-loud clusters. Additionally shown
  is the contribution of radio-quiet and radio-loud populations to the total RLF
  (assuming a fraction of 25 per cent and 1 per cent of radio-loud objects). The
  top right panel shows the RLF obtained by applying the observed
  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation {\bf (see Fig.~\ref{fig:PLSZ})}
  to the MultiDark clusters at $z = 0.2$, using our phenomenological gas model
  for $L_{\rmn{X,bol}}$ of each cluster; again for different percentages of
  radio-loud clusters.  The bottom left panel shows the RLF obtained by applying
  the observed $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$ relation {\bf (see
    Fig.~\ref{fig:PLSZ})} to the MultiDark clusters at $z = 0.2$, using
  $Y_{\rmn{SZ}, 500}$ of our our phenomenological gas model for each
  cluster. The bottom right panel shows the comparison between the three
  approaches for 10 per cent of radio-loud clusters. In all panels, we show the
  NVSS survey RLF \citep{1999NewA....4..141G} with a median redshift of
  $z\approx 0.18$, corrected for the sample incompleteness and survey sky
  coverage.  Horizontal error bars represent the mass bins while the vertical
  error bars are Poissonian uncertainties. The light gray line marked by the
  arrow estimates the incompleteness limit owing to the adopted low-mass cut (in
  the construction of the mock cluster catalog, see Paper~I) and the scatter in
  the halo luminosities.}
\label{fig:RLF_1.4}
\end{figure*}

>>>>

\begin{figure*} 
\centering
\includegraphics[width=0.85\textwidth]{figures/RLFs_1.4.eps}
\caption{RH luminosity function (RLF) at 1.4~GHz. The top left panel shows the
  RLF of our extended CR model (see main text for the details of the chosen
  parameters) for different fractions of radio-loud clusters. Additionally shown
  is the contribution of radio-quiet and radio-loud populations to the total RLF
  (assuming a fraction of 25 per cent and 1 per cent of radio-loud objects). The
  top right panel shows the RLF obtained by applying the observed
  $L_{1.4~\rmn{GHz}}-L_{\rmn{X,bol}}$ relation {\bf (see left panel of
    Fig.~\ref{fig:PLSZ})} to the MultiDark clusters at $z = 0.2$, using our
  phenomenological gas model for $L_{\rmn{X,bol}}$ of each cluster; again for
  different percentages of radio-loud clusters.  The bottom left panel shows the
  RLF obtained by applying the observed $L_{1.4~\rmn{GHz}}-Y_{\rmn{SZ}, 500}$
  relation {\bf (see right panel of Fig.~\ref{fig:PLSZ})} to the MultiDark
  clusters at $z = 0.2$, using $Y_{\rmn{SZ}, 500}$ of our our phenomenological
  gas model for each cluster. The bottom right panel shows the comparison
  between the three approaches for 10 per cent of radio-loud clusters. In all
  panels, we show the NVSS survey RLF \citep{1999NewA....4..141G} with a median
  redshift of $z\approx 0.18$, corrected for the sample incompleteness and
  survey sky coverage.  Horizontal error bars represent the mass bins while the
  vertical error bars are Poissonian uncertainties. The light gray line marked
  by the arrow estimates the incompleteness limit owing to the adopted low-mass
  cut (in the construction of the mock cluster catalog, see Paper~I) and the
  scatter in the halo luminosities.}
\label{fig:RLF_1.4}
\end{figure*}
